Incentivizing Exploration with Unbiased History

### 2018-11-02 model.tex
Minor edit to save a line.

\xhdr{Connection to multi-armed bandits.}
The special case when each message $m_t$ is an arm, and the $t$-th agent always chooses this arm, corresponds to a standard multi-armed bandit problem with IID rewards. Thus, regret in our problem can be directly compared to regret in the bandit problem with the same mean rewards $(\mu_a:\,a\in\A)$. Following the literature on bandits, we define the \emph{gap parameter} $\Delta$ as the difference between the largest and second largest mean rewards.%
\footnote{Formally, the second-largest mean reward is
    $\max_{a\in\A:\mu(a)<\mu^*} \mu(a)$,
where $\mu^* = \max_{a\in\A} \mu(a)$.
}
The gap parameter is not known to the principal (in our problem), or to the algorithm (in the bandit problem). Optimal regret rates for bandits with IID rewards are as follows \cite{bandits-ucb1,bandits-exp3,Lai-Robbins-85}:
\begin{align}\label{eq:model-OptRegret}
\reg(T) \leq O\left(\min\left(
    \sqrt{KT\log T},\; \tfrac{1}{\Delta} \log T
    \right)\right).
\end{align}
This regret bound can only be achieved using \emph{adaptive exploration}: \ie when exploration schedule is adapted to the observations. A simple example of \emph{non}-adaptive exploration is the \emph{explore-then-exploit} algorithm which samples arms uniformly at random for the first $N$ rounds, for some pre-set number $N$, then chooses one arm and sticks with it till the end. More generally,
\emph{exploration-separating} algorithms have a property that in each round $t$, either the choice of an arm does not depend on the observations so far, or the reward collected in this round is not used in the subsequent rounds. Any such algorithm suffers from $\Omega(T^{2/3})$ regret in the worst case.%
\footnote{The first explicit reference we are aware of is \cite{MechMAB-ec09,DevanurK09}, but this fact has been known in the community for much longer.}

>>>>

\xhdr{Connection to multi-armed bandits.}
The special case when each message $m_t$ is an arm, and the $t$-th agent always chooses this arm, corresponds to a standard multi-armed bandit problem with IID rewards. Thus, regret in our problem can be directly compared to regret in the bandit problem with the same mean rewards $(\mu_a:\,a\in\A)$. Following the literature on bandits, we define the \emph{gap parameter} $\Delta$ as the difference between the largest and second largest mean rewards.%
\footnote{Formally, the second-largest mean reward is
    $\max_{a\in\A:\mu(a)<\mu^*} \mu(a)$,
where $\mu^* = \max_{a\in\A} \mu(a)$.
}
The gap parameter is not known to the principal (in our problem), or to the algorithm (in the bandit problem). Optimal regret rates for bandits with IID rewards are as follows \cite{bandits-ucb1,bandits-exp3,Lai-Robbins-85}:
\begin{align}\label{eq:model-OptRegret}
\reg(T) \leq O\left(\min\left(
    \sqrt{KT\log T},\; \tfrac{1}{\Delta} \log T
    \right)\right).
\end{align}
This regret bound can only be achieved using \emph{adaptive exploration}: \ie when exploration schedule is adapted to the observations. A simple example of \emph{non}-adaptive exploration is the \emph{explore-then-exploit} algorithm which samples arms uniformly at random for the first $N$ rounds, for some pre-set number $N$, then chooses one arm and sticks with it till the end. More generally,
\emph{exploration-separating} algorithms have a property that in each round $t$, either the choice of an arm does not depend on the observations so far, or the reward collected in this round is not used in the subsequent rounds. Any such algorithm suffers from $\Omega(T^{2/3})$ regret in the worst case.%
\footnote{The first explicit reference we know of is \cite{MechMAB-ec09,DevanurK09}, but this fact has been known in the community for much longer.}
